LCA in R using tidySEM

### 2022-09-06 example_analysis/Daniel_LCA.Rmd
Update Daniel_LCA.Rmd

---
title: "LCA in R"
output: html_notebook
---

USING TIDYSEM:

see functions starting in mx

```{r}
library(tidySEM)
df <- data_mix_ordinal
df[1:4] <- lapply(df, ordered)
mx_lca(data = df,
       classes = 2) -> res
```

```{r}
res$class1
res$latentVars
```

>>>>

---
title: "LCA in R using tidySEM"
output: html_notebook
---

# LOADING THE DATASET

```{r}
library(tidySEM) 
df <- data_mix_ordinal #ask Caspar to rename the dataset in documentation
df[1:4] <- lapply(df, ordered)
```

# Exploring the data

```{r}
tidySEM::descriptives(df)
```

# Conduct latent class analysis

```{r}
# fitting the model
set.seed(123)
res <- mx_lca(data = df, classes = 1:4)
```
# Class enumeration

```{r}
# printing model fit table
fit_table <- table_fit(res)
fit_table[ , c("Name", "LL", "AIC", "BIC", "Entropy", "prob_min", "prob_max", "n_min", "n_max")]
```

# Interpreting class solution

```{r}
library(ggplot2)
plot_prob(res[[3]]) + scale_fill_manual(name = "bla")
table_prob(res[[3]])
```

# Extracting posterior class probabilities

```{r}
probs <- class_prob(res[[3]])
probs$mostlikely.class
probs$individual
```

# APPENDIX
